Dear Paul Robbins,

I hope this message finds you well. I am writing to express my enthusiastic interest in the Product Manager role at Clover Health, as advertised on your website. With a strong background in product management and a passion for making a positive impact in healthcare, I am excited about the opportunity to contribute to your team.

In my previous roles, I have successfully led product development initiatives and collaborated with cross-functional teams, including product triads, and look forward to add clinical teams. Through these experiences, I have gained valuable insights and developed strategies for delivering customer value as early as possible. My work on a freelance project for b.health involved writing UX copy to enhance the user experience of their platform. And I've built CRM features for BestForDentistry, which gave me with hands-on experience in providing valuable tools for dental practitioners.

I am particularly drawn to Clover Health's mission of improving healthcare access and outcomes for all. I believe that my skills in product management, coupled with my understanding of the healthcare industry, make me well-suited to contribute to your team's success.

Thank you for considering my application. I am eager to further discuss how my background and experiences align with the needs of the Product Manager role at Clover Health. I am available at your earliest convenience for an interview and can be reached via email at venhamon@gmail.com.

Looking forward to the possibility of joining the Clover Health team and making a meaningful impact together.

Warm regards,

Benji